\section{File Description}

In the \emph{encodings} folder you can find the actual encoding used for the experimental evaluation. Since for comparison purposes we focus on DECLARE, the constraints are directly referred by name. The ASP-based representations of the automata corresponding to the DECLARE constraints used in the experiments are in \texttt{templates.lp}. Note that, although the encodings of the data-aware version of the problems (denoted by \texttt{\_data.lp} in the file name) can be used to solve the control-flow-only version as well in the folder is present also a simplified encoding tailored to this version.\\

In the \emph{real\_data} folder there are the 8 real dataset organized in folders. In each of them, together with the XES file there are also the discovered models in declare format and the ASP version of all such files. Note that while the models have the usual extension .lp, the log has extension .asp but is just a regular ASP file. This is done simply to make them easily recognizable and to facilitate the automation of the experiments with a script.\\

In the \emph{synth\_data} folder are present the 4 reference models used for log generation and conformance checking, together with their control-flow-only version. Note how in the latter is dealt with the local conditions to make possible to use the data-aware encoding. Again, it is possible to directly use the tailored encoding. In the folder are also present the logs of size 1000 and traces of varying length used for conformance checking and query checking. Finally, for query checking are present the files with a possible query, the relative conditions and the set of activities. File \texttt{activities.lp} needs to be used also for log generation with reference models since, being always the same, they were not included in the model itself. \\

In the \emph{utils} folder are present files with functions for performing different useful tasks, like converting from .xes and .decl to ASP files. However this has already been performed for our datasets. 